Pattern matching for\\ $(213,231)$-avoiding permutations

### 2015-02-05 article.tex
modification : proof for both permutation in avoiding 213 213 remove : corollary 2

\begin{corollary}
Let $\pi \in \AV_n(213,231)$. We have
$$
\stripe{\pi}{i} =
\begin{cases}
			\ustep & \text{if $\pi[i]$ is the minimal element of $\pi[i:]$}\\    
			\dstep & \text{if $\pi[i]$ is the maximal element of $\pi[i:]$}\\
	\end{cases}
	$$
\end{corollary}

@@

\begin{proof} 
	The forward direction is obvious.
	We prove the backward direction by induction on the size of the motif
	$\sigma$.
	The base case is a motif of size 2. Suppose that we have the motif $(12)$, thus the stripe of the motif is $\ustep$. If there is a match in stripe, then there exists two (contiguous) increasing elements in the text, which is a match in permutation. Same goes for the permutation $(21)$. Now, suppose that the lemma is true for every motif in $\Av{n}{(231,213)}$. Let $\pmotif$ be a motif in $\Av{n+1}{(231,213)}$, and $\ptext$ a permutation avoiding $(213,231)$. If there is a match of $\stripew{\pmotif}$ in $\stripew{\ptext}$ by subsequence $s$, then there is a match of $\stripew{\pmotif}[2:]$ in $\stripew{\ptext}[2:]$ by subsequence $s[2:]$, and by induction there is a match of $\pmotif[2:]$ in $\ptext[2:]$ by subsequence $s[2:]$. Moreover if the first element the stripe of the motif is ascend (descent), and by lemma \ref{lemma:first element is 1 or n} the minimal (maximal) element, and remark that a subsequence of a permutation avoiding (231,213) is also avoiding (231,213), thus the first element of the subsequence $s$ is either the minimal (maximal) element which complete our proof.
\qed
\end{proof}

@@

\begin{proof}
To solve the permutation pattern for a permutation in $\AV_n(213,231)$, 
we find a find a match of the stripe of the pattern in the stripe of the text.
This can be done linearly by a greedy algorithm, 
by matching a step whenever it is possible.
And thank to the definition of the definition of a stripe in \textbf{Corollary \ref{corollary:minmaxelement}},
we do not have to compute the stripe advance.
Therefore we have an linear (online) algorithm.
\end{proof}

>>>>

@@

\begin{proof} 
	The forward direction is obvious.
	We prove the backward direction by induction on the size of the motif
	$\sigma$.
	The base case is a motif of size 2. Suppose that we have the motif $(12)$, thus the stripe of the motif is $\ustep$. If there is a match in stripe, then there exists two (contiguous) increasing elements in the text, which is a match in permutation. Same goes for the permutation $(21)$. Now, suppose that the lemma is true for every motif in $\Av{n}{(231,213)}$. Let $\pmotif$ be a motif in $\Av{n+1}{(231,213)}$, and $\ptext$ a permutation avoiding $(213,231)$. Suppose that there is a match of $\stripew{\pmotif}$ in $\stripew{\ptext}$, Let's $s$ be the subsequence such that $\stripew{\pmotif}$ occurs in $\stripew{\ptext}$.
	By induction $\pmotif[2:]$ appears in $\ptext$ by subsequence $s[2:]$.
	Moreover if the first element the stripe of the motif is ascend (descent), then by lemma \ref{lemma:first element is 1 or n} the first element is the minimal (maximal) element. Remark that a subsequence of a permutation avoiding (231,213) is also avoiding (231,213), thus the first element of the subsequence $s$ is either the minimal (maximal), element which complete our proof.
\qed
\end{proof}

@@

\begin{proof}
To solve the permutation pattern for a permutation in $\AV_n(213,231)$, 
we find a find a match of the stripe of the pattern in the stripe of the text.
This can be done linearly by a greedy algorithm, 
by matching a step whenever it is possible.
And thank to the definition of the definition of a stripe in \textbf{Corollary \ref{corollary:minmaxelement}},
we do not have to compute the stripe in advance.
Therefore we have an linear (online) algorithm.
\end{proof}
